ZCB Pricing

### 2018-07-28 ZCB Pricing .Rmd
Cleaned up some code. Modified the finite difference methods to produce one price. Added some more chunks

```{r 1}
# Closed form solution to Bond price

bond_price <- function(alpha=0.08,beta=0.8,sigma=0.005,t=0,T=5,r=0.08){
  A <- (1-exp(-beta*(T-t)))/(beta)
  B <- (1/beta)*((alpha-(sigma)^2/(2*beta))*(A - T +t) - (sigma^(2)*A^2)/(4))
  exp(-A*r +B)
}

@@

# Crude Monte Carlo

Crude_Monte_Carlo=function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=100){

  # alpha, beta, sigma <- Fixed Parameters
  # T <- maturity time
  # r <- Initial rate at time 0
  # n <- Number of Simulations
  # s <- NUmber of Sub-intervals over time

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path = matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r # Initial rates on first row.

@@

Antithetic_variates = function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r = 0.08,n=1000,s=100){
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using negative values of RV
  sim_path[1,] = r
  sim_path_inv[1,] = r
  z = rnorm(n) # Generate standard normal values
  z. = -z # Estimate negative value

@@

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt) # The Sum and Sum. variables record the summation of their respective rates to approximate the integral
  Sum.=colSums(sim_path_inv[2:(s+1),]*dt)
  int=exp(-Sum.) #Exponential of the estimate
  int.=exp(-Sum) #Exponential of the estimate under the negative rv 
  Average=(int+int.)/2   # The average of the expressions is taken for new estimate
  mean=mean(Average)  # The average of the expression is taken for the estimate
  sd=sd(Average)/sqrt(n)
  result= mean
  result

@@

```{r 4}
#################################################################################
# Moment matching
#################################################################################

Moment_Matching=function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=100000,s=100){

  # alpha, beta, sigma <- Fixed Parameters
  # T <- maturity time
  # r0 <- Initial rate at time 0
  # n <- Number of Simulations
  # s <- NUmber of Subintervals

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r0
  z=rnorm(n)
  z_m= z-mean(z) # MOMENT MATCHING TRANSFORMATION

@@

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  int=exp(-Sum)
  mean=mean(int)
  sd=sd(int)/sqrt(n)
  result=mean
  result
}

@@

```{r 5}
#################################################################################
# Control Variates
#################################################################################

# We have decided to make use of the CIR model as our control variate process.
# Below is the closed form solution under the CIR model
bond_price_CIR <- function(alpha,beta,sigma,t,T,r0){
  h <- sqrt(alpha^(2)+2*sigma^(2))
  A <-(2*h*exp((alpha+h)*(T-t)/2)/(2*h+(alpha+h)*(exp((T-t)*(h))-1)))^((2*alpha*beta)/sigma^(2))
  B <-2*(exp((T-t)*(h))-1)/(2*h+(alpha+h)*(exp((T-t)*(h))-1))
  A*exp(-B*r0)
}

@@

CIR_MC= function(alpha,beta,sigma,T,r0,n,s){

  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r0

@@

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  int=exp(-Sum)
  mean=mean(int)
  sd=sd(int)/sqrt(n)
  result=c(mean,sd)
  result

@@

Control_Variates_estimate= function(alpha, beta, sigma,t,T,r0,n,s){
  Crude_Monte_Carlo(alpha,beta,sigma,T,r0,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r0,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r0)
}

@@

```{r 6}

#======================================================================================
# Doing some plots

xvec <- seq(-0.3,0.5,0.01)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
}

CR <- NULL
AV <- NULL
MM <- NULL

for (k in 1: length(xvec)){
  CR[k] <- Crude_Monte_Carlo(r0 = xvec[k], T=5)
}

for (s in 1: length(xvec)){
  AV[s] <- Antithetic_variates(r0 = xvec[s], T =5)

for (j in 1: length(xvec)){
  MM[j] <- Moment_Matching(r0 = xvec[j], T =5)

plot(CR, x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Monte Carlo vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
lines(xvec,AV, col ="black", lty =1.5)
lines(xvec,MM, col ="yellow", lty =1.5)
```

```{r 7}
# Explicit Method

explicit = function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:1250, J =seq(-0.4,0.6,0.005),T=5){

  M <- length(J)
  N <- length(I)

  dt <- T/N
  dr <- J[2] -J[1]

@@

  Diag_1 <- matrix(0,ncol = M, nrow = M)
    # Main diagonal of matrix 1

@@

  # Filling lower diagonal of matrix 1
  for (j in 2:M){
    Diag_1[j,j-1] <- pd(j)
  }

  # Filling upper diagonal of matirx 1
  for (j in 1:(M-1)){
    Diag_1[j,j+1] <- pu(j)
  }

  Bond_values <- matrix(1,nrow=M, ncol =1)

  for (i in I){
    Bond_values <- Diag_1%*%Bond_values
    Bond_values <- Bond_values
  }

  index = match(as.character(r),xvec)
  Bond_values[index]
}

#============================================================================================
#Doing some plots
# 
#  xvec <- seq(-0.4,0.6,0.005)
# S <- NULL
# for (i in 1:length(xvec)){
#    S[i] <- bond_price(alpha = 0.08,beta =0.8,sigma =0.005,t = 0, T = 5, r = xvec[i])
#  }
#  
# H <- explicit(r = 0.08, I= 1:100000, T=5,alpha = 0.08, beta =0.8, sigma= 0.005, J = xvec)
# 
#  
#  plot(H, x = xvec,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Explicit vs Known Solution")
#  lines(xvec,S, col ="blue", lty =1.5)

@@

```{r 8}

# Implicit Method

implicit <- function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:1250, J =seq(-0.4,0.6,0.005),T=5){
  # I = partition of time interval
  # J = partition of short rate variable

  nr <- length(J) # number of rows based on rate grid points
  nc <- length(I) # number of columns based on number of time grid points

  dr <- J[2] - J[1] #length of each sub-interval across J
  dt <- T/length(I) #length of each sub-interval across I

@@

  pd <- function(j){
    dt*((alpha-beta*J[j+1])/(2*dr) - (sigma^2)/(2*dr^2))

@@

  pm <- function(j){
    dt*(J[j+1] + 1/dt +sigma^2/(dr^2))
  }

  pu <- function(j){
    -dt*((alpha-beta*J[j+1])/(2*dr) + (sigma^2)/(2*dr^2))

@@

  # Setting up tridiagonal matrix
  Diag <- matrix(0,nrow = nr-1,ncol = nr-1)

  # Filling main diagonal
  for (j in 1:(nr-1)){
    Diag[j,j] <- pm(j)

  # Filling lower diagonal
  for (j in 2:(nr-1)){
    Diag[j,j-1] <- pd(j)
  }

  # Filling upper diagonal
  for (j in 1:(nr-2)){
    Diag[j,j+1] <- pu(j)
  }

  B <- matrix(1,ncol = 1,nrow = nr-1) # The matrix of bond prices at maturity time

  for (i in I){
    C <- matrix(0,ncol = 1, nrow = nr-1) # Another matrix for boundary conditions
    C[nr-1,1] <- (-pu(nr-1))*B[nr-1,1]
    C[1,1] <- -pd(1)
    A <- B  # Working backwards recursively 
    B <- solve(Diag)%*%A 
  }

  #B # Output of bond prices at time 0 for varying rates
  index = match(as.character(r),xvec)
  B[index]
}

#============================================================================================

# Doing some plots

# xvec <- seq(-0.4,0.6,0.005)
# R <- implicit(T=5,J= xvec, I = 1:1250)
# S <- NULL
# for (r in 1:length(xvec)){
#   S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
#   }
# plot(R, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
# lines(xvec,S, col ="blue", lty =1.5)

@@

```{r 9}
# Crank-Nicholson Method

CN <- function(alpha = 0.08, beta = 0.8, sigma = 0.005, r = 0.08, T =5 , I = 1:1250, J = seq(-0.4,0.8,0.005)){
  # I = partition of time interval
  # J = partition of short rate interval

  M <- length(J)
  N <- length(I)

  dt <- T/N
  dr <- J[2] -J[1]
  #===========================================================================================
  # Define the following functions for j = 1,...,M at each time point i

@@

  # Main diagonal of matrix 2
  for (j in 1:M){
    Diag_2[j,j] <- -1/dt + pm(j)

@@

  for (i in I){

@@

  #Bond_values

  index = match(as.character(r),xvec)
  Bond_values[index]
}

#============================================================================================
# Doing some plots

# xvec <- seq(-0.4,0.8,0.005)
# S <- NULL
# for (r in 1:length(xvec)){
#   S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
# }
# plot(CN(), x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
# lines(xvec,S, col ="blue", lty =1.5)
```

```{r 11}

@@

```{r 12, echo = FALSE}
# Comparison of results
# Varying short rates

compare_mat <- matrix(NA,nrow = 10, ncol = 10) # matrix of comparison

colnames(compare_mat) <- c("Alpha","Beta","Sigma","Initial rate","Known Price","Monte Carlo"," MC System Time","MC Squared Deviations", "Moment Matching", "System Time")

for (j in 1:10){
  compare_mat[j,1] <- 0.08
  compare_mat[j,2] <- 0.8
  compare_mat[j,3] <- 0.005
  compare_mat[j,4] <- 0.01 +0.01*(j-1)
  compare_mat[j,5] <- bond_price(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], t= 0, T = 1, r = compare_mat[j,4])
  start_time <- proc.time()[1]
  compare_mat[j,6] <- Crude_Monte_Carlo(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], T = 1, r0 = compare_mat[j,4], n = 1000, s=250)
  compare_mat[j,7] <- proc.time()[1] -start_time
  compare_mat[j,8] <- (compare_mat[j,6] -compare_mat[j,5])^2
  start_time <- proc.time()[1]
  compare_mat[j,9] <- Moment_Matching(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], T = 1, r0 = compare_mat[j,4], n = 1000, s=250)
  compare_mat[j,10] <- proc.time()[1] - start_time

@@

>>>>

```{r 1}
# Closed form solution of the Bond price

bond_price <- function(alpha=0.08,beta=0.8,sigma=0.005,t=0,T=5,r=0.08){
  # alpha, beta, sigma <- Fixed Parameters
  # T <- maturity time
  # r <- Initial rate at time 0  
  A <- (1-exp(-beta*(T-t)))/(beta)
  B <- (1/beta)*((alpha-(sigma)^2/(2*beta))*(A - T +t) - (sigma^(2)*A^2)/(4))
  exp(-A*r +B)
}

@@

# Crude Monte Carlo function

Crude_Monte_Carlo = function(alpha = 0.08, beta = 0.8, sigma = 0.005, T = 5, r = 0.08, n = 1000, s = 200){

  # alpha, beta, sigma <- Fixed Parameters
  # T <- maturity time
  # r <- Initial rate at time 0
  # n <- Number of Simulations
  # s <- NUmber of Subintervals over time

  #Simulate interest rates
  dt <- T/s # Length of subintervals
  sim_path = matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r # Initial rates on first row.

@@

Antithetic_variates = function(alpha = 0.08, beta = 0.8, sigma = 0.005, T = 5, r = 0.08, n = 1000, s = 200){

  dt <- T/s # Length of subintervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using negative values of RV
  sim_path[1,] = r
  sim_path_inv[1,] = r
  z = rnorm(n) # Generate standard normal values
  z. = -z # Estimate negative value

@@

  # Monte Carlo Simulations
  Sum = colSums(sim_path[2:(s+1),]*dt) # The Sum and Sum. variables record the summation of their respective rates to approximate the integral
  Sum.= colSums(sim_path_inv[2:(s+1),]*dt)
  int = exp(-Sum.) #Exponential of the estimate
  int.= exp(-Sum) #Exponential of the estimate under the negative rv 
  Average = (int+int.)/2   # The average of the expressions is taken for new estimate
  mean = mean(Average)  # The average of the expression is taken for the estimate
  sd =sd(Average)/sqrt(n)
  result = mean
  result

@@

```{r 4}

# Moment matching

Moment_Matching = function(alpha = 0.08, beta = 0.8, sigma = 0.005, T = 5,r = 0.08, n = 1000, s = 200){

  # alpha, beta, sigma <- Fixed Parameters
  # T <- maturity time
  # r <- Initial rate at time 0
  # n <- Number of Simulations
  # s <- NUmber of Subintervals

  #Simulate interest rates
  dt <- T/s # Length of subintervals
  sim_path = matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r
  z = rnorm(n)
  z_m = z-mean(z) # MOMENT MATCHING TRANSFORMATION

@@

  # Monte Carlo Simulations
  Sum = colSums(sim_path[2:(s+1),]*dt)
  int = exp(-Sum)
  mean = mean(int)
  sd = sd(int)/sqrt(n)
  result= mean
  result
}

@@

```{r 5}

# Control Variates

# We have decided to make use of the CIR model as our control variate process.
# Below is the closed form solution under the CIR model
bond_price_CIR <- function(alpha, beta, sigma, t, T, r){
  h <- sqrt(alpha^(2)+2*sigma^(2))
  A <-(2*h*exp((alpha+h)*(T-t)/2)/(2*h+(alpha+h)*(exp((T-t)*(h))-1)))^((2*alpha*beta)/sigma^(2))
  B <-2*(exp((T-t)*(h))-1)/(2*h+(alpha+h)*(exp((T-t)*(h))-1))
  A*exp(-B*r)
}

@@

CIR_MC= function(alpha  = 0.08, beta = 0.8, sigma = 0.005, T = 5, r = 0.08, n = 1000, s = 200){

  dt <- T/s # Length of subintervals
  sim_path = matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,] = r

@@

  # Monte Carlo Simulations
  Sum = colSums(sim_path[2:(s+1),]*dt)
  int = exp(-Sum)
  mean = mean(int)
  sd = sd(int)/sqrt(n)
  result = mean
  result

@@

Control_Variates_estimate = function(alpha = 0.08, beta = 0.8, sigma = 0.005,t = 0,T = 5,r = 0.08,n = 1000,s = 200){
  Crude_Monte_Carlo(alpha,beta,sigma,T,r,n,s)- CIR_MC(alpha,beta,sigma,T,r,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r)
}

@@

```{r 6}
# Explicit Method

explicit = function(alpha = 0.08,beta = 0.8, sigma = 0.005,r = 0.08, I = 1:1250, J = seq(-0.4,0.6,0.005),T = 5){

  # I = partition of time interval
  # J = partition of short rates sequence

  M <- length(J) # Number of short rate grid points
  N <- length(I) # Number of time grid poiints

  dt <- T/N # Lenght of each time subinterval
  dr <- J[2] -J[1] # Lenght of each time interval

@@

  #Setting up tridiagonal matrix

  Diag_1 <- matrix(0,ncol = M, nrow = M)
    # Main diagonal of matrix

@@

  # Filling lower diagonal of matrix 
  for (j in 2:M){
    Diag_1[j,j-1] <- pd(j)
  }

  # Filling upper diagonal of matirx 
  for (j in 1:(M-1)){
    Diag_1[j,j+1] <- pu(j)
  }

  # Bond price values at maturity are all 1 unit   
  Bond_values <- matrix(1,nrow=M, ncol =1)

  # Working backwards in time
  for (i in 1:(length(I)+1)){
    Bond_values <- Diag_1%*%Bond_values
    Bond_values <- Bond_values
  }

  # Finding index of the desired short rate
  index = match(as.character(r),J)
  # Output is the corresponding bond price at time 0
  Bond_values[index]
}

@@

```{r 7}
# Implicit Method

implicit <- function(alpha = 0.08,beta = 0.8,sigma = 0.005,r = 0.08,I = 1:1250, J =seq(-0.4,0.6,0.005),T=5){

  # I = partition of time interval
  # J = partition of short rate variable

  M <- length(J) # Number of short rate grid points
  N <- length(I) # Number of time grid poiint

  dr <- J[2] - J[1] # length of each sub-interval across J
  dt <- T/N # length of each sub-interval across I

@@

  pd <- function(j){
    dt*((alpha-beta*J[j])/(2*dr) - (sigma^2)/(2*dr^2))

@@

  pm <- function(j){
    dt*(J[j] + 1/dt +sigma^2/(dr^2))
  }

  pu <- function(j){
    -dt*((alpha-beta*J[j])/(2*dr) + (sigma^2)/(2*dr^2))
  }

  # Setting up tridiagonal matrix
  Diag <- matrix(0,nrow = M,ncol = M)

  # Filling main diagonal
  for (j in 1:M){
    Diag[j,j] <- pm(j)

@@

  # Filling lower diagonal
  for (j in 2:M){
    Diag[j,j-1] <- pd(j)
  }

  # Filling upper diagonal
  for (j in 1:(M-1)){
    Diag[j,j+1] <- pu(j)
  }

  Bond_values <- matrix(1,ncol = 1,nrow = M) # The matrix of bond prices at maturity time 
  Inv <- solve(Diag) # Inverse of tridiagonal matrix

  for (i in 1:(length(I) +1)){
    C <- matrix(0,ncol = 1, nrow = M) # Another matrix for boundary conditions
    C[M,1] <- (-pu(M))*Bond_values[M,1]
    C[1,1] <- -pd(1)

    RHS <- Bond_values  # Working backwards recursively 
    Bond_values <- Inv%*%RHS
  }

  # Finding index of the desired short rate
  index = match(as.character(r),J)
  # Output is the corresponding bond price at time 0
  Bond_values[index]
}

@@

```{r 8}
# Crank-Nicholson Method

CN <- function(alpha = 0.08, beta = 0.8, sigma = 0.005, r = 0.08, T = 5 , I = 1:1250, J = seq(-0.4,0.6,0.005)){

  M <- length(J) # Number of short rate grid points
  N <- length(I) # Number of time grid poiints

  dt <- T/N # Length of each time subinterval
  dr <- J[2] -J[1] # Lenght of each rate subinterval
  #===========================================================================================
  # Define the following functions for j = 1,...,M at each time point i

@@

  # Main diagonal of matrix 2
  for (j in 1:M){
    Diag_2[j,j] <- -1/dt + pm(j)
    }

@@

  for (i in 1:(length(I)+1)){

@@

  # Index of rate corresponding to desired short rate
  index = match(as.character(r), J)
  # Output corresponding to desired short rate
  Bond_values[index]
}

@@

```{r 9}
# Modified Fully Implicit Method

```{r 10}
# Plots of the different methods
par(mfrow = c(2,2))

xvec <- seq(-0.4,0.6,0.005) # Vector for rates

known_sol <- NULL # Vector to hold the known closed form solution
for (r in 1:length(xvec)){
  known_sol[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
}

CR <- NULL # Vector to hold Crude Monte Carlo Solutions
AV <- NULL # Vector to hold Antithetic Monte Carlo Solutions
MM <- NULL # Vector to hold Moment Matching  Carlo Solutions
CV <- NULL # Vector to hold Control Variates Monte Carlo Solutions

Expl <- NULL # Vector to hold Explicit method Solutions
Impl <- NULL # Vector to hold Implicit method Solutions
Crank <- NULL # Vector to hold Crank-Nicolson Solutions

# Plots of Monte Carlo Methods ----------------------------------------------------------------------

for (i in 1: length(xvec)){
  CR[i] <- Crude_Monte_Carlo(r = xvec[i])
}

for (i in 1: length(xvec)){
  AV[i] <- Antithetic_variates(r = xvec[i])
}

for (i in 1: length(xvec)){
  MM[i] <- Moment_Matching(r = xvec[i])
}

for (i in 1: length(xvec)){
  CV[i] <- Control_Variates_estimate(r = xvec[i])
}

plot(CR, x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Monte Carlo Solutions vs Known Solution")
lines(xvec, known_sol, col ="blue", lty =1.5)
lines(xvec, AV, col ="black", lty =1.5)
lines(xvec, MM, col ="yellow", lty =1.5)
lines(xvec, CV, col ="green", lty =1.5)

# Plots of Finite Difference Methods ----------------------------------------------------------------------

for (i in 1: length(xvec)){
  Expl[i] <- explicit(r = xvec[i])
}

for (i in 1: length(xvec)){
  Impl[i] <- implicit(r = xvec[i])
}

for (i in 1: length(xvec)){
  Crank[i] <- CN(r = xvec[i])
}

plot(Expl, x = xvec ,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Explicit Method vs Known Solution")
lines(xvec, known_sol, col ="blue", lty =1.5)

plot(Impl, x = xvec ,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
lines(xvec, known_sol, col ="blue", lty =1.5)

plot(Crank, x = xvec ,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank-Nicolson Method vs Known Solution")
lines(xvec, known_sol, col ="blue", lty =1.5)

```{r 11, echo = FALSE}
# Comparison of results for numerical methods

compare_mat <- matrix(NA,nrow = 7, ncol = 4) # matrix of comparison

colnames(compare_mat) <- c("Price", "Known Price", "Error", "System Time")
rownames(compare_mat) <- c("Crude Monte Carlo", "Antithetic Variates", "Moment Matching", "Control Variates", "Explicit Method", "Implicit Method", "Crank-Nicolson Method")

compare_mat[,2] <- bond_price()

# Crude Monte Carlo
start_time <- proc.time()[1]
compare_mat[1,1] <- Crude_Monte_Carlo()
compare_mat[1,4] <- proc.time()[1] - start_time
compare_mat[1,3] <- compare_mat[1,2] - compare_mat[1,1]

# Antithetic Variates
start_time <- proc.time()[1]
compare_mat[2,1] <- Antithetic_variates()
compare_mat[2,4] <- proc.time()[1] - start_time
compare_mat[2,3] <- compare_mat[2,2] - compare_mat[2,1]

# Moment Matching
start_time <- proc.time()[1]
compare_mat[3,1] <- Moment_Matching()
compare_mat[3,4] <- proc.time()[1] - start_time
compare_mat[3,3] <- compare_mat[3,2] - compare_mat[3,1]

# Control Variates
start_time <- proc.time()[1]
compare_mat[4,1] <- Control_Variates_estimate()
compare_mat[4,4] <- proc.time()[1] - start_time
compare_mat[4,3] <- compare_mat[4,2] - compare_mat[4,1]

# Explicit method
start_time <- proc.time()[1]
compare_mat[5,1] <- explicit()
compare_mat[5,4] <- proc.time()[1] - start_time
compare_mat[5,3] <- compare_mat[5,2] - compare_mat[5,1]

# Implicit method
start_time <- proc.time()[1]
compare_mat[6,1] <- implicit()
compare_mat[6,4] <- proc.time()[1] - start_time
compare_mat[6,3] <- compare_mat[6,2] - compare_mat[6,1]

# Crank-Nicolson method
start_time <- proc.time()[1]
compare_mat[7,1] <- CN()
compare_mat[7,4] <- proc.time()[1] - start_time
compare_mat[7,3] <- compare_mat[7,2] - compare_mat[7,1]

@@

```{r 12}
# Sensitivity Tests
